Spectroscopic confirmation of very-wide stellar binaries and large-separation comoving pairs from \textsl{Gaia DR1}

### 2017-07-29 paper/comoving-followup.tex
fixing some other issues

\begin{table}[ht]
  \begin{center}
    \begin{tabular}{ c | c }
      \toprule
        Parameter & Prior \\\toprule
        $\ln A$ & $\mathcal{U}(2, 16)$\\
        $x_0$ & $\mathcal{U}(6547, 6579)$\\
        $\ln\sigma_G$ & $\mathcal{U}(-4, 2)$\\
        $\ln\gamma_L$ & $\mathcal{U}(-4, 2)$\\
        $\alpha_1$ & $\mathcal{U}(0, 10^{16})$\\
        $\alpha_2$ & $\mathcal{U}(-10^8, 10^8)$\\
        $\ln\sigma_{3/2}$ & $\mathcal{U}(-8, 8)$\\
        $\ln\rho_{3/2}$ & $\mathcal{N}(1, 1)$\\
      \bottomrule
    \end{tabular}
    \caption{
      Priors used for \Ha\ line profile model parameters.
      $\mathcal{U}(a, b)$ indicates a uniform prior between $a$ and $b$ and
      $\mathcal{N}(\mu, \sigma^2)$ indicates a normal distribution with mean
      $\mu$ and variance $\sigma^2$.
      Wavelength units are all angstroms.
      \todo{what are the flux units?}
      \smoh{A column of brief description of parameters would be useful.}
      \label{tbl:prior-bounds}
    }
  \end{center}
\end{table}

@@

\todo{TESS-HERMES}
An additional 202 candidate comoving pairs (\citealt{Oh:2017}) have
previously-measured radial velocities (for each star) reported in \DR{5} of the
Radial Velocity Experiment (RAVE; \citealt{Kunder:2017}).
Using the same procedure described in \sectionname~\ref{sec:catalog}, we
identify confirmed comoving pairs using the RAVE velocities for all pairs within
$200~\pc$ and find a similar false-positive rate at large separations ($\approx
38\%$ are confirmed).
Of the \nraveoverlap\ RAVE-overlap candidate comoving pairs (within $200~\pc$)
that meet the above criteria, we find \nravecomoving\ confirmed comoving pairs.
We plot the confirmed comoving pairs identified through radial velocity
follow-up in this work along with the RAVE-confirmed pairs in
\figurename~\ref{fig:separation-RAVE}.
Top histogram shows the separation (chord length) distribution for the joint
sample, scatter plot shows log-chord-length and the pair distances, and right
histogram shows the distance distribution of the confirmed pairs.
At larger distances ($\gtrsim 150~\pc$) it appears that the detection efficiency
of our method drops, as expected given the hard cut in log-FML-ratio applied to
define the candidate sample.
Reassuringly, there do not appear to be any trends of the chord length
distribution with distance.

@@

\subsection{Caveats} \label{sec:caveats}

The results presented in this work demonstrate that even at separations larger
than a parsec, a substantial fraction of comoving pair candidates selected from
astrometry alone are confirmed with three-dimensional velocity information.
This is exciting because it confirms the existence of what is likely a
population of nearly-coherent but unbound coeval stars.
It is also encouraging for the prospect of selecting large samples of comoving
pairs purely with astrometric data from future data releases of the \gaia\
mission (radial velocity measurements will only be released for bright stars, $G
< 12$).
However, in this work, we do not claim to report the true number or density of
large-separation comoving pairs.
To model the abundance and formation of comoving pairs, it will be crucial to
select larger samples of pairs without hard cuts on separation, tangential
velocity, signal-to-noise, or likelihood ratio, as were done with the input
sample used in this work.

@@

% Need precise chemical information

% But at very large separations, how do you convince yourself that a pair was truly coeval? Same chemistry? To what precision? What about chemical differences from planet formation?

% Going forward, will have to use hierarchical mixture models to study population of singles in conjunction

% Great reward: Once chemical homogeneity understood amongst stars of same spectral type, can be used to calibrate stellar models across the HR diagram: should have same age, chemistry, etc. Also tests of chemical enrichment due to planetary systems

% Abundances - future work, Coronado in prep.! But: throw shade on abundances
% because planet engulfment (https://arxiv.org/pdf/1707.02180.pdf). Also Oh et al.
% 2017b

@@

% \subsection{Prospects for Galactic structure} \label{sec:dynamics}

\subsection{Future spectroscopic surveys} \label{sec:future-rvs}

DISCO / AS4, 4MOST, WEAVE, DESI, PFS

@@

It is a pleasure to thank
Ruth Angus (Columbia),
John Brewer (Yale),
Jason Curtis (Columbia),
Keith Hawkins (Columbia),
David W. Hogg (NYU),
Melissa Ness (MPIA), and
Dave Zurek (AMNH)
for useful discussions and advice.
We thank James Davenport (WWU) for releasing his open source spectroscopic
reduction code, \package{PyDIS}, which served as inspiration for the pipeline
used in this work.
This work is based on observations obtained at the MDM Observatory, operated by
Dartmouth College, Columbia University, Ohio State University, Ohio University,
and the University of Michigan.
This work has made use of data from the European Space Agency (ESA)
mission {\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed by
the {\it Gaia} Data Processing and Analysis Consortium (DPAC,
\url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding
for the DPAC has been provided by national institutions, in particular
the institutions participating in the {\it Gaia} Multilateral Agreement.
This research has made use of the SIMBAD database, operated at CDS, Strasbourg,
France.
% The authors are pleased to acknowledge that the work reported on in this
% paper was substantially performed at the TIGRESS high performance computer
% center at Princeton University which is jointly supported by the Princeton
% Institute for Computational Science and Engineering and the Princeton
% University Office of Information Technology's Research Computing department.

>>>>

\begin{table}[ht]
  \begin{center}
    \begin{tabular}{ c | c | l }
      \toprule
        Parameter & Prior & Description \\\toprule
        $\ln A$ & $\mathcal{U}(2, 16)$ & Logarithm of line amplitude
          [${\rm photons}$]\\
        $x_0$ & $\mathcal{U}(6547, 6579)$ & Line wavelength centroid
          [${\rm \AA}$]\\
        $\ln\sigma_G$ & $\mathcal{U}(-4, 2)$ & Logarithm of Gaussian standard
          deviation of line profile [${\rm \AA}$]\\
        $\ln\gamma_L$ & $\mathcal{U}(-4, 2)$ & Logarithm of Lorentzian HWHM of
          line profile\\
        $\alpha_1$ & $\mathcal{U}(0, 10^{16})$ & Background model offset at line
          centroid [${\rm photons}$]\\
        $\alpha_2$ & $\mathcal{U}(-10^8, 10^8)$ & Background model slope
          [${\rm photons}~{\rm \AA}^{-1}$]\\
        $\ln\sigma_{3/2}$ & $\mathcal{U}(-8, 8)$ & Logarithm of Gaussian process
          amplitude [${\rm photons}$]\\
        $\ln\rho_{3/2}$ & $\mathcal{N}(1, 1)$ & Logarithm of Gaussian process
          correlation scale [${\rm \AA}$]\\
      \bottomrule
    \end{tabular}
    \caption{
      Priors used for \Ha\ line profile model parameters.
      $\mathcal{U}(a, b)$ indicates a uniform prior between $a$ and $b$ and
      $\mathcal{N}(\mu, \sigma^2)$ indicates a normal distribution with mean
      $\mu$ and variance $\sigma^2$.
      Flux units are photons, i.e. the spectra are not flux-calibrated.
      \label{tbl:prior-bounds}
    }
  \end{center}
\end{table}

@@

An additional 202 candidate comoving pairs (\citealt{Oh:2017}) have
previously-measured radial velocities (for each star) reported in \DR{5} of the
Radial Velocity Experiment (RAVE; \citealt{Kunder:2017}).
Using the same procedure described in \sectionname~\ref{sec:catalog}, we
identify confirmed comoving pairs using the RAVE velocities for all pairs within
$200~\pc$ and find a similar false-positive rate at large separations ($\approx
38\%$ are confirmed).
Of the \nraveoverlap\ RAVE-overlap candidate comoving pairs (within $200~\pc$)
that meet the above criteria, we find \nravecomoving\ confirmed comoving pairs.
We plot the confirmed comoving pairs identified through radial velocity
follow-up in this work along with the RAVE-confirmed pairs in
\figurename~\ref{fig:separation-RAVE}.
Top histogram shows the separation (chord length) distribution for the joint
sample, scatter plot shows log-chord-length and the pair distances, and right
histogram shows the distance distribution of the confirmed pairs.
At larger distances ($\gtrsim 150~\pc$) it appears that the detection efficiency
of our method drops, as expected given the hard cut in log-FML-ratio applied to
define the candidate sample.
Reassuringly, there do not appear to be any trends of the chord length
distribution with distance.

@@

% \subsection{Caveats and additional validation} \label{sec:caveats}

The results presented in this work demonstrate that even at separations larger
than a parsec, a substantial fraction of comoving pair candidates selected from
astrometry alone are confirmed with three-dimensional velocity information.
This is exciting because it confirms the existence of what is likely a
population of nearly-coherent but unbound coeval stars.
It is also encouraging for the prospect of selecting large samples of comoving
pairs purely with astrometric data from future data releases of the \gaia\
mission (radial velocity measurements will only be released for bright stars, $G
< 12$).
However, in this work, we do not claim to report the true number or density of
large-separation comoving pairs.
To model the abundance and formation of comoving pairs, it will be crucial to
select larger samples of pairs without hard cuts on separation, tangential
velocity, signal-to-noise, or likelihood ratio, as were done with the input
sample used in this work.
It will also be important to quantify the contamination rate of (3D) comoving
pair lookalikes, especially at large separations.

We do not try to estimate a contamination rate in this work, but instead use
metallicities and radial velocities from 61 candidate comoving pairs that are in
\DR{3} of the \acronym{LAMOST} survey (\citealt{Deng:2012}) as an additional
validation test.
\figurename~\ref{fig:lamost} shows these pairs plotted as the difference in
radial velocity and difference in iron abundance with points colored by the
chord length separation of each pair.
There is a clear over-density of pairs with abundance and radial-velocity
differences close to zero.
From this figure it is also clear that the false positives are predominantly the
largest separation pairs (i.e. are the darkest markers), but a number of
$>1~\pc$ pairs appear to have small radial-velocity differences and small
differences in iron abundances, making them even more likely to be genuine
pairs.

\begin{figure}[htbp]
  \begin{center}
    \includegraphics[width=0.9\linewidth]{lamost.pdf}
  \end{center}
  \caption{%
    Stuff
    \label{fig:lamost}}
\end{figure}

Going forward, definitive confirmation of comoving star pairs may require
precise measurements of chemical abundances combined with precise radial
velocities, as demonstrated with the \acronym{LAMOST} data.
However, we would also like to \emph{test} assumptions about chemical
homogeneity, rather than simply assuming that all true comoving pairs must have
identical abundances.
For example, the outcomes of planet formation may lead to large or appreciable
abundance differences between coeval stars (e.g., \citealt{yo}, Oh et al.,
submitted).
We therefore caution that---to study the chemical properties of comoving pairs
and star formation in general---the comoving pairs should be selected from their
kinematics alone.

@@

@@

% \subsection{Future spectroscopic surveys} \label{sec:future-rvs}

% DISCO / AS4, 4MOST, WEAVE, DESI, PFS

@@

It is a pleasure to thank
Ruth Angus (Columbia),
John Brewer (Yale),
Jason Curtis (Columbia),
Keith Hawkins (Columbia),
David W. Hogg (NYU),
Melissa Ness (MPIA), and
Dave Zurek (AMNH)
for useful discussions and advice.
We thank James Davenport (WWU) for releasing his open source spectroscopic
reduction code, \package{PyDIS}, which served as inspiration for the pipeline
used in this work.
This work is based on observations obtained at the MDM Observatory, operated by
Dartmouth College, Columbia University, Ohio State University, Ohio University,
and the University of Michigan.
This work has made use of data from the European Space Agency (ESA)
mission {\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed by
the {\it Gaia} Data Processing and Analysis Consortium (DPAC,
\url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding
for the DPAC has been provided by national institutions, in particular
the institutions participating in the {\it Gaia} Multilateral Agreement.
This research has made use of the SIMBAD database, operated at CDS, Strasbourg,
France.
% The authors are pleased to acknowledge that the work reported on in this
% paper was substantially performed at the TIGRESS high performance computer
% center at Princeton University which is jointly supported by the Princeton
% Institute for Computational Science and Engineering and the Princeton
% University Office of Information Technology's Research Computing department.
Guoshoujing Telescope (the Large Sky Area Multi-Object Fiber Spectroscopic
Telescope LAMOST) is a National Major Scientific Project built by the Chinese
Academy of Sciences. Funding for the project has been provided by the National
Development and Reform Commission. LAMOST is operated and managed by the
National Astronomical Observatories, Chinese Academy of Sciences.
